%-------------------------
% Resume in Latex
% Author : Michael Jordan
% Based off of: https://github.com/jakegut/resume/resume.tex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue
    }
\input{glyphtounicode}


%----------FONT OPTIONS----------
%\renewcommand{\rmdefault}{cmtt}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeCompany}[3]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 & #3 \\
    \end{tabular*}
}

\newcommand{\resumePosition}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.96\textwidth}[t]{p{9cm}p{6cm}@{\extracolsep{\fill}}r}
      #1 & \textit{#2} & \textit{#3} \\
    \end{tabular*}
}

\newcommand{\resumeEducation}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{ #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSentences}[1]{
  \vspace{-10pt}\item
    \begin{flushleft}
      \textit{\small{#1}} \\
    \end{flushleft}
}

\newcommand{\resumeEducationTwo}[8]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{ #4} \\
      \small{#5} & #6 \\
      \small{#7} & #8
    \end{tabular*}\vspace{-8pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeEducationListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeEducationListEnd}{\end{itemize}}
\newcommand{\resumeCompaniesListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeCompaniesListEnd}{\end{itemize}}
\newcommand{\resumePositionListStart}{\begin{itemize}[leftmargin=0.075in, label={}]\vspace{-6pt}}
\newcommand{\resumePositionListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=-]}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeSentencesListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSentencesListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%-----------Name + Contact-----------
\begin{center}
    \textbf{\Huge \scshape Michael Jordan} \\
    \small +44 7480-743079 $|$ \href{mailto:mgjordan314@gmail.com}{\underline{mgjordan314@gmail.com}} $|$
    \href{https://github.com/MGJordan}{\underline{github.com/MGJordan}}
\end{center}\vspace{-20pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeEducationListStart
    \resumeEducationTwo
      {Imperial College}{London, UK}
      {Master of Science (MSc) in Ecology, Evolution, and Conservation (Distinction)}{2023–2024}{- Dissertation using DNA metabarcoding and barcoding to measure biodiversity. Coded in R.}{}
      {- Coursework in Geographic Information Systems (GIS), Genomics, Carbon Cycle, Advanced Statistics.}{}
    \resumeEducation
      {Harvard University}{Cambridge, MA, USA}
      {Bachelor of Arts (BA) in Economics}{2004–2008}{}
  \resumeEducationListEnd\vspace{-5pt}
    

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeCompaniesListStart

    \resumeCompany{Google / Alphabet}{}{}

        \resumePositionListStart
        
          \resumePosition{Business Analyst Manager - YouTube}{Singapore}{2021–2023}
            \resumeItemListStart
              \resumeItem{Managed 3-person team providing data and statistical analysis for Trust \& Safety content moderation operations (policy enforcement decision quality, vendor utilization) for an $\sim$400 person org with 24/7 global coverage. Collaborated with cross-functional Directors to set annual goals and quarterly objectives and key results (OKRs). Owned insights in VP-level forum. Planned and led strategy offsite. Mentored team for professional development.}
              \resumeItem{Restructured team time management away from low value-add tasks and toward thought leadership by reducing operational and technical debt (streamlined processes to allow stakeholders to self-service, won stakeholder buy-in on service level agreements, clarified roles \& responsibilities, worked with Data Engineering to improve upstream data, increased rigor of coding standards). Reduced time spent on manual tasks and bug bashing by over 50\%.}
              \resumeItem{Collaborated with Detection Engineering and Global Scaled Operations to synthesize disparate processes into a method to capture cost savings opportunities created by increases in machine-learning model precision and recall.}
            \resumeItemListEnd
    
          \resumePosition{Senior Business Analyst - YouTube}{Singapore}{2019–2021}
            \resumeItemListStart
              \resumeItem{Owned data and statistical analysis for Trust \& Safety content moderation global operations. Developed metrics, generated actionable insights for VP and Director-level stakeholders, coded Structured Query Language (SQL) data pipelines in a production environment, project-managed cross-functional initiatives, conducted root cause analysis into metric trends, conducted sensitivity analysis, worked with real-time and time series data, wrote business requirement documents (BRDs), built visualizations and dashboards. Earned level promotion.}
              \resumeItem{Developed and scaled a vendor utilization metric (defined metric, won buy-in from cross-functional stakeholders, coded SQL pipeline, built reporting, owned roll-out). Collaborated with cross-functional stakeholders to project-manage initiatives that increased utilization from 55\% to 85\%, preventing $\sim$\$45M/year in lost spend.}
              \resumeItem{Coded SQL pipeline to support COVID business contingency planning. Caught and prevented multiple P0 bugs.}
            \resumeItemListEnd
        
        \resumePosition
          {Financial Analyst - Android}{Singapore}{2017–2019}
          \resumeItemListStart
            \resumeItem{Owned financial planning and analysis (FP\&A) for Android partnerships in Asia-Pacific. Designed valuation models in Google Sheets. Owned partnership deal approval. Provided actionable insights to business development team. Contributed analysis to strategic plans and pitch decks. Coded data pipelines in SQL, R, and Python.}
          \resumeItemListEnd
          
        \resumePosition
          {Solutions Consultant - gTech}{Cambridge, MA / NYC, NY, USA}{2012–2017}
          \resumeItemListStart
            \resumeItem{Debugged Display Network bidding algorithm and conversion tracking issues for clients and internal stakeholders. Queried SQL databases. Conducted A/B tests. Contributed to product development.  Earned level promotion.}
          \resumeItemListEnd
    
        \resumePositionListEnd

  \resumeCompaniesListEnd

  \resumeSentencesListStart
  
      \resumeSentences
      {Experience prior to 2012 includes analytical roles at two venture-backed startups, Meebo (social media and digital advertising) and Mindset Media (advertising tech), as well as in management consulting at Alliance Consulting Group.}
      
  \resumeSentencesListEnd
  

%-----------Skills-----------
\vspace{-5pt}\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages, Software, \& OS}{: SQL, R, some Python, some Bash, Google Sheets, Microsoft Excel, Windows, Linux} \\
     \textbf{Software Development Tools}{: Git, Visual Studio Code} \\
     \textbf{Statistics}{: Causal Inference (e.g., t-test, F-test, chi-squared test), Supervised Machine Learning (e.g., GLMs such as Logistic Regression, Mixed Models), Unsupervised Machine Learning (e.g., PCA, PCoA, NMDS, K-means clustering)} \\
     \textbf{Bioinformatics Software \& Systems}{: BLAST, BOLD, LULU, DADA2, IDTAXA, GeneiousPrime} \\
     \textbf{Molecular Biology}{: DNA Extraction, PCR, Gel Electrophoresis, NGS (MiSeq), Sanger Sequencing}
    }}
 \end{itemize}

%-----------Interests-----------
\vspace{-16pt}\section{Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Endurance Sports (Personal Best)}{: Ironman (13:33:37), half Ironman (5:16:24), marathon (2:58:40), 5K (18:43)} \\
     \textbf{Volunteering}{: \href{https://twc2.org.sg/}{Transient Workers Count Too}, \href{https://www.rosiesplace.org/}{Rosie's Place}, \href{https://maralliance.org/}{MarAlliance}, \href{https://www.nss.org.sg/}{Singapore Nature Society}} \\
     %\textbf{Favorite Recent Book}{: \href{https://www.goodreads.com/book/show/59575939-an-%immense-world}{An Immense World: How Animal Senses Reveal the Hidden Realms Around Us}}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}