%-------------------------
% Resume in Latex
% Author : Michael Jordan
% Based off of: https://github.com/jakegut/resume/resume.tex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue
    }
\input{glyphtounicode}


%----------FONT OPTIONS----------
%\renewcommand{\rmdefault}{cmtt}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeCompany}[3]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 & #3 \\
    \end{tabular*}
}

\newcommand{\resumePosition}[3]{
  \item
    \begin{tabular*}{0.96\textwidth}[t]{p{9cm}p{6cm}@{\extracolsep{\fill}}r}
      #1 & \textit{#2} & \textit{#3} \\
    \end{tabular*}
}

\newcommand{\resumeEducation}[6]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{ #4} \\
      \small{#5} & #6
    \end{tabular*}
}

\newcommand{\resumeEducationTwo}[8]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{ #4} \\
      \small{#5} & #6 \\
      \small{#7} & #8
    \end{tabular*}
}

\newcommand{\resumeEducationThree}[5]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{@{\extracolsep{\fill}}lccl}
      \textbf{#1} & \textit{#2} & {#3} & {#4} \\
    \end{tabular*}
    \begin{tabular*}{0.97\textwidth}[t]{l}
      \small{#5}
    \end{tabular*}
}

\newcommand{\resumeSentences}[1]{
  \item
    \begin{flushleft}
      \textit{\small{#1}} \\
    \end{flushleft}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeEducationListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeEducationListEnd}{\end{itemize}}
\newcommand{\resumeCompaniesListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeCompaniesListEnd}{\end{itemize}}
\newcommand{\resumePositionListStart}{\begin{itemize}[leftmargin=0.075in, label={}]\vspace{-6pt}}
\newcommand{\resumePositionListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=-]}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeSentencesListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSentencesListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%-----------Name + Contact-----------
\begin{center}
    \textbf{\Huge \scshape Michael Jordan} \\
    \small +44 7480-743079 $|$ Based in London, UK $|$ \href{mailto:mgjordan314@gmail.com}{\underline{mgjordan314@gmail.com}} $|$
    \href{https://github.com/MGJordan}{\underline{github.com/MGJordan}}
\end{center}

  \resumeSentencesListStart
  
      \resumeSentences
      {Tech leader in data \& analytics. Left Google voluntarily in 2023 for a career sabbatical to pursue a personal interest in ecology by enrolling in a full-time graduate program.}
      
  \resumeSentencesListEnd\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeEducationListStart
    \resumeEducationThree
      {Imperial College}{MSc in Ecology (Distinction)}
      {London, UK}{2023–2024}
      {- Coursework in Machine Learning, Advanced Statistics, Genomics, Carbon Cycle, GIS.}\vspace{-5pt}
    \resumeEducationThree
      {Harvard University}{BA in Economics}
      {Cambridge, MA, USA}{2004–2008}{- Coursework in Econometrics, Statistics, Linear Algebra, Corporate Finance, Capital Markets.}
  \resumeEducationListEnd\vspace{-15pt}
    

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeCompaniesListStart

    \resumeCompany{Google}{}{}

        \resumePositionListStart
        
          \resumePosition{Business Analyst Manager - YouTube}{Singapore}{2021–2023}
            \resumeItemListStart
              \resumeItem{Analytics Lead (L5) owning data and statistical analysis into operations (enforcement decision quality, vendor operations) for YouTube Trust \& Safety ($\sim$400 person org requiring 24/7 global coverage).}
              \resumeItem{Managed 3-person BA team supporting business metrics (metric development, causal inference testing, root cause analysis, strategic advisory). Set annual goals, quarterly OKRs, and KPIs in collaboration with cross-functional Directors. Ran strategy offsite. Mentored team for professional development.}
              \resumeItem{Collaborated with Directors of Detection Engineering and Vendor Operations to develop a model to capture vendor cost savings opportunities created by detection ML model improvements. \textbf{Saved \$2M-\$4M in vendor cost in typical headcount governance cycle}.}
              \resumeItem{Reduced operational and technical debt by streamlining processes, collaborating with Data Engineering team to improve upstream data, and aligning with stakeholders on SLAs and R\&R. \textbf{Cut time spent bug-bashing by 53\%}.}
            \resumeItemListEnd
    
          \resumePosition{Senior Business Analyst - YouTube}{Singapore}{2019–2021}
            \resumeItemListStart
              \resumeItem{Owned data and statistical analysis into vendor operations for YouTube Trust \& Safety.}
              \resumeItem{Coded production SQL pipelines using BigQuery to query large (\textgreater 1 TB) datasets, developed business metrics, conducted hypothesis tests and root cause analysis into metric trend shifts using R and Python in Colab, owned actionable insights in VP and Director forums, built visualizations using Google Data Studio. \textbf{GoogleSQL readability. Level promotion.}}
              \resumeItem{Developed a vendor utilization metric. Defined metric, won stakeholder buy-in, coded SQL pipelines, built visualizations, trained FTEs. Project-managed initiatives to increase utilization in collaboration with cross-functional stakeholders. \textbf{Increased utilization from 55\% to 85\%, preventing \$45M in otherwise wasted spend annually}.}
              \resumeItem{Supported COVID-19 business contingency planning by rapidly coding production SQL pipelines to detect failures in operational systems. \textbf{Caught multiple P0/OMG bugs} that would have caused wide-scale content moderation failures.}
            \resumeItemListEnd
        
        \resumePosition
          {Financial Analyst - Android}{Singapore}{2017–2019}
          \resumeItemListStart
            \resumeItem{Owned financial planning and analysis for Asia-Pacific Android partnerships. Modeled customer LTV using Google Sheets. Coded business metric pipelines and forecast trends using Python. Conducted hypothesis tests using R. Supported Business Development team with financial analysis for pitch decks. Owned deal and PO approval. Coded SQL pipelines.}
          \resumeItemListEnd
          
        \resumePosition
          {Technical Product Expert - gTech}{Cambridge, MA, USA}{2014–2017}
          \resumeItemListStart
            \resumeItem{Debugged issues in Google Ads bidding algorithms, conversion tracking, and ad targeting. Conducted A/B experiments. Collaborated with Product teams to inform feature development. Queried SQL databases. \textbf{Level promotion.}}
          \resumeItemListEnd

        \resumePosition
          {Optimization Specialist - gTech}{NYC, NY, USA}{2012–2014}
          \resumeItemListStart
            \resumeItem{Analyzed Google Ads Dynamic Remarketing campaigns to improve performance (CTR, conversion rate, CPA). Supported internal Sales teams and external clients.}
          \resumeItemListEnd
    
        \resumePositionListEnd

  \resumeCompaniesListEnd

  \resumeSentencesListStart
  
      \resumeSentences
      {Experience prior to 2012 includes analytical roles at Meebo (social media), Mindset Media (ad tech), and Alliance Consulting.}
      
  \resumeSentencesListEnd
  

%-----------Skills-----------
\vspace{-15pt}\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages, Software, \& OS}{: SQL, R, Python, Bash, Spreadsheets, Windows, Linux} \\
     \textbf{Development \& BI Tools}{: Version Control (Git), Bug Tracking, SSH, IDEs (Visual Studio Code), Data Visualization (Google Data Studio, Tableau), Cloud Data Warehousing (BigQuery), Jupyter Notebooks (Colab)} \\
     \textbf{Statistics \& ML}{: Causal Inference, Linear Modeling, Dimensionality Reduction, Clustering, Classification, Model Selection}
    }}
 \end{itemize}

%-----------Interests-----------
\vspace{-15pt}\section{Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Endurance Sports (Personal Best)}{: Ironman (13:33:37), half Ironman (5:16:24), marathon (2:58:40), 5K (18:43)} \\
     \textbf{Volunteering}{: \href{https://twc2.org.sg/}{Transient Workers Count Too}, \href{https://www.rosiesplace.org/}{Rosie's Place}, \href{https://maralliance.org/}{MarAlliance}, \href{https://www.nss.org.sg/}{Singapore Nature Society}} \\
     %\textbf{Favorite Recent Book}{: \href{https://www.goodreads.com/book/show/59575939-an-%immense-world}{An Immense World: How Animal Senses Reveal the Hidden Realms Around Us}}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}